Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2020-01-16 Manuscript/Figures/figure_legends.Rmd

**Figure 1. Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** (A) Unique boundaries are denoted by the blue dots. The linear genome was subsequently binned into resolution-specific intervals. The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$). (B) Three types of associations between bins and genomic annotations (green shapes) used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.

>>>>

**Figure 1. Illustrating the resolution-specific data construction and feature engineering used for downstream modeling.** Unique boundaries are denoted by the blue dots. The linear genome was subsequently binned into resolution-specific intervals. The response vector **Y** was defined as a genomic bin that either overlapped with a TAD boundary ($Y = 1$) or did not ($Y = 0$). Three types of associations between bins and genomic annotations (green shapes) were then used to build the feature space of random forest classification models include _Overlap Counts_ (OC), _Overlap Percent_ (OP), and ($log_{2}$) _Distance_.

### 2020-01-16 Manuscript/manuscript.Rmd

$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}.$$
To give the sets of boundaries A and B dimensionality to enable us to calculate overlap, we flank each boundary point by a flanking factor, *f*=5000.

>>>>

$$J_{(A,B)} = \dfrac{A \cap B}{A \cup B}.$$
To give the sets of boundaries A and B dimensionality to enable us to calculate overlap, we flank each boundary point by a flanking factor, $f=max\{r_{A},r_{B}\}$, where $r_{A(B)}$ is the Hi-C data resolution used to call TADs for A (B).
